Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-18 cordillera-cycle.tex
Add record scaling factors.

% tab:records
\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters used to
           prepare temperature offset time-series used to force the ice sheet
           model through the last 120\,kyr. $T_{[32;22]}$ refers to the
           mean temperature anomaly during the period -32 to~-22~kyr after
           scaling.}
  \label{tab:records}
  {\begin{tabular}{lcccc}
    \tophline
    Record & Proxy & Scaling factor & $T_{[32;22]}$ & Original reference\\
    \middlehline
    GRIP     & \chem{\delta^{18}O} & ?\% & -5.8{\degree}C
        & \citet{Dansgaard.etal.1993} \\
    NGRIP    & \chem{\delta^{18}O} & ?\% & -6.1{\degree}C
        & \citet{Andersen.etal.2004} \\
    EPICA    & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C
        & \citet{Jouzel.etal.2007} \\
    Vostok   & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C
        & \citet{Petit.etal.1999} \\
    ODP~1012 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C
        & \citet{Herbert.etal.2001} \\
    ODP~1020 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C
        & \citet{Herbert.etal.2001} \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

>>>>

% tab:records
\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters used to
           prepare temperature offset time-series used to force the ice sheet
           model through the last 120\,kyr. $T_{[32;22]}$ refers to the
           mean temperature anomaly during the period -32 to~-22~kyr after
           scaling.}
  \label{tab:records}
  {\begin{tabular}{lcccc}
    \tophline
    Record & Proxy & Scaling factor & $T_{[32;22]}$ & Original reference\\
    \middlehline
    GRIP     & \chem{\delta^{18}O} & 0.35 & -5.8{\degree}C  % -16.4126
        & \citet{Dansgaard.etal.1993} \\
    NGRIP    & \chem{\delta^{18}O} & 0.22 & -6.1{\degree}C  % -26.7098
        & \citet{Andersen.etal.2004} \\
    EPICA    & \chem{\delta^{18}O} & 0.60 & -5.6{\degree}C  % -9.2055
        & \citet{Jouzel.etal.2007} \\
    Vostok   & \chem{\delta^{18}O} & 0.70 & -5.6{\degree}C  % -7.9550
        & \citet{Petit.etal.1999} \\
    ODP~1012 & \chem{U^{K'}_{37}}  & 1.53 & -5.8{\degree}C  % -3.7889
        & \citet{Herbert.etal.2001} \\
    ODP~1020 & \chem{U^{K'}_{37}}  & 1.16 & -5.8{\degree}C  % -5.0000
        & \citet{Herbert.etal.2001} \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}
